Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-18 paper2_JNLS/Referee Reports/Ref1Response/Ref1.tex
NM

\begin{itemize}
\item First, thank you for these insightful comments. The referee is correct that a sufficient amount of nonlinear interaction is  required for relaxation to the Gibbs measure. We agree that it is most likely the failure of this condition being met that explains the discrepancy between formula (53) and the smallest-amplitude data in Fig. 8(c). We have inserted these points in the updated manuscript. First, see the passage in Section 3.5 (page 11):
\begin{quotation}
We also point out that a sufficient amount of nonlinear mixing is required for relaxation to the above Gibbs measure. In the linearized system, for example, modes propagate without interacting and hence the initial measure induced by the wave generator remains unchanged.
\end{quotation}
Second, see the passage describing Fig. 8(c) in Section 4.4 (page 22)
\begin{quotation}
The apparently less predictable behavior at small amplitudes can be attributed to the fact that, in order for the system to relax to the Gibbs measure, modes must interact through nonlinearity. For the smallest amplitude experiments, the amount of nonlinearity is apparently too small for  modes to mix sufficiently.
\end{quotation}
%
\item We thank the referee for drawing our attention to the vibrant field of integrable turbulence. We have now included a discussion to compare and contrast our statistical theory with that from integrable turbulence (as well as a few additional references). In particular, please see the new passage at the end of section 3.4
\begin{quotation}
We comment on some important differences between the KdV and TKdV dynamical systems. Besides momentum, energy, and Hamiltonian, KdV possesses in infinite sequence of additional invariants. Trajectories of KdV are therefore constrained by an infinite number of conserved quantities, associated with the fact that it is a completely integrable system whose long-time dynamics are dominated by coherent structures known as solitons. The analogues of these additional invari- ants, however, are not generally conserved in the truncated system; the only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Dynamics of TKdV, rather than being dominated by coherent structures, become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though a rigorous mathematical proof awaits) [2]. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence [54, 40, 10, 41], where integrability is exploited to uncover certain statistical features. We remind the reader that KdV is asymptotically valid only for large spatial scales and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV should be regarded as on equal footing as far as physical realism, provided that sufficiently many modes are considered. Where differences exist in long-time dynamics, it is unclear a priori which model, if either, more closely resembles reality, which underscores the importance of controlled laboratory experiments.
\end{quotation}
\end{itemize}
%\item The referee is correct that equilibrium statistical mechanics and the canonical ensemble is used here, not because it is rigorously justified, but as an effective theory that explains the data.

>>>>

\begin{itemize}
\item Thank you for these insightful comments which have helped us to improve the discussion of the Gibbs measure throughout the paper. We have added revisions to several key places of the paper, detailed as follows:
\item First, The referee is correct that a sufficient amount of nonlinear interaction is  required for relaxation to the Gibbs measure. We agree that it is most likely the failure of this condition being met that explains the discrepancy between formula (53) and the smallest-amplitude data in Fig. 8(c). We have inserted these points in the updated manuscript. First, see the passage in Section 3.5 (page 11):
\begin{quotation}
We also point out that a sufficient amount of nonlinear mixing is required for relaxation to the above Gibbs measure. In the linearized system, for example, modes propagate without interacting and hence the initial measure induced by the wave generator remains unchanged.
\end{quotation}
Second, see the passage describing Fig. 8(c) in Section 4.4 (page 22)
\begin{quotation}
The apparently less predictable behavior at small amplitudes can be attributed to the fact that, in order for the system to relax to the Gibbs measure, modes must interact through nonlinearity. For the smallest amplitude experiments, the amount of nonlinearity is apparently too small for  modes to mix sufficiently.
\end{quotation}
%
\item We thank the referee for drawing our attention to the vibrant field of integrable turbulence. We have now included a discussion to compare and contrast our statistical theory with those stemming from integrable turbulence (and included a few key references). In particular, please see the new passage at the end of section 3.4
\begin{quotation}
We comment on some important differences between the KdV and TKdV dynamical systems. Besides momentum, energy, and Hamiltonian, KdV possesses in infinite sequence of additional invariants. Trajectories of KdV are therefore constrained by an infinite number of conserved quantities, associated with the fact that it is a completely integrable system whose long-time dynamics are dominated by coherent structures known as solitons. The analogues of these additional invari- ants, however, are not generally conserved in the truncated system; the only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Dynamics of TKdV, rather than being dominated by coherent structures, become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though a rigorous mathematical proof awaits) [2]. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence [54, 40, 10, 41], where integrability is exploited to uncover certain statistical features. We remind the reader that KdV is asymptotically valid only for large spatial scales and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV should be regarded as on equal footing as far as physical realism, provided that sufficiently many modes are considered. Where differences exist in long-time dynamics, it is unclear a priori which model, if either, more closely resembles reality, which underscores the importance of controlled laboratory experiments.
\end{quotation}
\end{itemize}
%\item The referee is correct that equilibrium statistical mechanics and the canonical ensemble is used here, not because it is rigorously justified, but as an effective theory that explains the data.

### 2020-05-18 paper2_JNLS/paper.tex
NM

\new{We comment on some important differences between the KdV and TKdV dynamical systems. Besides momentum, energy, and Hamiltonian, KdV possesses in infinite sequence of additional invariants. Trajectories of KdV are therefore constrained by an infinite number of conserved quantities, associated with the fact that it is a completely integrable system whose long-time dynamics are dominated by coherent structures known as solitons. The analogues of these additional invariants, however, are {\em not} generally conserved in the truncated system; the only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Dynamics of TKdV, rather than being dominated by coherent structures, become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though a rigorous mathematical proof awaits) \cite{bajars2013weakly}. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence \cite{zakharov2009turbulence, randoux2014intermittency, costa2014soliton, randoux2016nonlinear}, where  integrability is exploited to uncover certain statistical features. We remind the reader that KdV is asymptotically valid only for large spatial scales and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV should be regarded as on equal footing as far as physical realism, provided that sufficiently many modes are considered. Where differences exist in long-time dynamics, it is unclear {\em a priori} which model, if either, more closely resembles reality, underscoring the importance of controlled laboratory experiments.
}

>>>>

\new{We comment on some important differences between the KdV and TKdV dynamical systems. Besides momentum, energy, and Hamiltonian, KdV possesses in infinite sequence of additional invariants \cite{lax1975periodic, whitham2011linear}. Trajectories of KdV are therefore constrained by an infinite number of conserved quantities, associated with the fact that it is a completely integrable system whose long-time dynamics are dominated by coherent structures known as solitons. The analogues of the additional invariants, however, are {\em not} generally conserved in the truncated system; the only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Dynamics of TKdV, rather than being dominated by coherent structures, become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though a rigorous proof awaits) \cite{bajars2013weakly}. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence \cite{zakharov2009turbulence, randoux2014intermittency, costa2014soliton, randoux2016nonlinear}, where  integrability is exploited to uncover certain statistical features of the system at hand. We remind the reader that KdV is asymptotically valid only for large spatial scales, and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV are on equal footing as far as physical realism -- a more accurate framework would require either model closure to capture the small scale physics or else direct numerical simulation of the Euler equations. Where differences exist between KdV and TKdV, therefore, it is unclear {\em a priori} which model, if either, more closely resembles reality. This situation, of course, underscores the importance of controlled laboratory experiments.
}
